Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Miscellaneous revisions.

Neither the DNS nor the SNI can be blocked without
collaterally blocking the front domain.
The Host header is unknown to the censor,
but known to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.

For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
A skilled censor will use both means of censorship,
and effective circumvention requires countering both.

@@

There are two general strategies for countering DPI.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Well-traveled look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
They both work by superenciphering a stream, using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send anything
until the client proves knowledge of shared secret, depriving the censor
of an easy distinguisher.
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

The other strategy against content blocking is the steganographic approach: look like
something the censor doesn't block.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP,
in order to match a firewall's whitelist.
StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy, which decodes it and forwards it to the destination.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

@@

\meekserver\ is a special-purpose web server.
When \meekserver\ receives a request, it extracts the body and feeds it into
a local Tor running as a bridge.
If there are any data pending to be sent back to the client from Tor,
\meekserver\ includes it in the body of the HTTP response.
\meekserver\ also handles session management:
as there may be many clients using the service at once,
the server must determine which client session each incoming request belongs to.
% It does this by means of an X-Session-ID header,
% described in this section.

@@

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-ID header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-ID headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

There are many parts of the TLS handshake, but the two that
most distinguish the client are the list of ciphersuites and the
list of TLS extensions in the Client Hello.
Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
differs in different client implementations.
Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
using the built-in crypto/tls library of the Go programming language.
The list of ciphersuites is unlike that of a web browser,
and could be used as a fingerprint for blocking.
Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
Similarly the list of TLS extensions (not shown)
differed between \meekclient\ and popular browsers.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.}
\label{fig:clients}
\end{figure}

Figure~\ref{fig:clients} shows the number of concurrent users of meek between January and May~2014,
as reported by the Tor Metrics Portal~\cite{metrics-meek}.
The number of concurrent users is estimated by counting directory requests made over the transport~\cite{counting-daily-bridge-users}.
The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.

>>>>

Neither the DNS nor the SNI can be blocked without
collaterally blocking the front domain.
The Host header is unknown to the censor,
but known to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

@@

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
A savvy censor will use both means of censorship---therefore
effective circumvention requires countering both.

@@

There are two general strategies for countering DPI.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Well-traveled look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
They both work by superenciphering a stream, using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send anything
until the client proves knowledge of shared secret, depriving the censor
of an easy distinguisher.
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

The other strategy against DPI is the steganographic approach: look like
something the censor doesn't block.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP,
in order to match a firewall's whitelist.
StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy, which decodes it and forwards it to the destination.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

@@

\meekserver\ is a special-purpose web server.
When \meekserver\ receives a request, it extracts the body and feeds it into
a local Tor running as a bridge.
If there are any data pending to be sent back to the client from Tor,
\meekserver\ includes it in the body of the HTTP response.
\meekserver\ also handles session management:
as there may be many clients using the service at once,
the server must determine which client session each incoming request belongs to.
% It does this by means of an X-Session-Id header,
% described in this section.

@@

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-Id header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

There are many parts of the TLS handshake, but the two that
most distinguish the client are the list of ciphersuites and the
list of TLS extensions in the ClientHello.
Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
differs in different client implementations.
Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
using the built-in crypto/tls library of the Go programming language.
The list of ciphersuites is unlike that of a web browser,
and could be used as a fingerprint for blocking.
Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
Similarly the list of TLS extensions (not shown)
differed between \meekclient\ and popular browsers.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

% Censor could lean on the CDN to block the actual destination internally.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Concurrent users of meek with Tor.}
\label{fig:clients}
\end{figure}

Figure~\ref{fig:clients} shows the average number of concurrent users of meek with Tor
since close to the beginning of development,
as reported by the Tor Metrics Portal~\cite{metrics-meek}.
The number of users is estimated by counting the number
of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by meek.
